\documentclass[12pt]{article}
\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[textwidth=12cm,centering]{geometry}
\usepackage[x11names]{xcolor}
\usepackage{background}
\usepackage{calligra}

\newcommand*\wb[3]{%
  {\fontsize{#1}{#2}\usefont{U}{webo}{xl}{n}#3}}

% The page frame
\SetBgColor{Goldenrod3}
\SetBgAngle{0}
\SetBgScale{1}
\SetBgOpacity{1}
\SetBgContents{%
\begin{tikzpicture}
\node at (0.5\paperwidth,0) {\wb{80}{34}{E}\rule[60pt]{.125\textwidth}{0.4pt}%
  \raisebox{55pt}{%
  \makebox[.75\textwidth]{\ \fontsize{24}{29}\selectfont\scshape Cocktail Selection}}%
  \rule[60pt]{.125\textwidth}{0.4pt}\wb{80}{34}{F}};
\node at (2,-0.5\textheight) {\rule{0.4pt}{.8\textheight}};
\node at (19.5,-0.5\textheight) {\rule{0.4pt}{.8\textheight}};
\node at (0.5\paperwidth,-\textheight) {\wb{80}{34}{G}\rule[-10pt]{\textwidth}{0.4pt}\wb{80}{34}{H}} ;
\end{tikzpicture}%
}

% colorize text
\newcommand*\ColText[1]{\textcolor{Goldenrod3}{#1}}

% a tabular* for each food group
\newenvironment{Group}[1]
  {\noindent\begin{tabular*}{\textwidth}{@{}p{\linewidth}@{\extracolsep{\fill}}c@{}}
    {\fontsize{24}{29}\selectfont\ColText{#1}}\\[1.0em]}
  {\end{tabular*}}

% to format each entry
\newcommand*\Entry[2]{%
 \centering{\calligra\large #1} & #2}

% to format each subentry
\newcommand*\Expl[1]{%
\centering{\calligra#1}}

\pagestyle{empty}

\begin{document}

\begin{Group}{}

\vspace{2.0em}
\Entry{\textbf{Myrtle Berry Flip}}\\
\Expl{A refreshing mix of myrtle berry (mirte bessen) liqueur, gin, and a citrus base. This cocktail combines the dominant herbal notes of myrtle berry with the freshness of a neutral spirit, balanced by the sweetness of cherry.}
\vspace{2.0em}

\Entry{\textbf{Manila Julep}}\\
\Expl{Southern hospitality meets the far East. A Southern US classic of fresh mint leaves under Bulliet rye whiskey topped off with a splash of dark rum and orange twist.}
\vspace{2.0em}


\Entry{\textbf{Singani Sour}}\\
\Expl{An exotic take on a true classic. This drink is reminiscent of a pisco or amaretto sour but uses Singani Brandy (imported from Bolivia) as its base. A perfect choice for a complex flavor derived from both Pechaud and Angostura bitters.}
\vspace{2.0em}


\Entry{\textbf{Sazerac}}\\
\Expl{The New Orleans classic! Rye or Bourbon whiskey poured over a pastis wash. Sweetened and spiced with Pechaud bitters (imported from Louisianna, USA)}
\vspace{2.0em}

\Entry{\textbf{Katherine's Compot}}\\
\Expl{Produced in-house; this rhubarb, strawberry, and apple compot is made with organically grown green apples. Infused with our finest Dutch gin.\\
Also available alcohol-free.} \\
\end{Group}

\vfill

\end{document}